---
title: "MiniProject6"
author: "Junfeng Guo"
date: "November 28, 2018"
output: pdf_document
---


## R Markdown
```{r question1}
#read the cancer data
cancer_dat <- read.table(file = "C:/Users/gjf19/Downloads/prostate_cancer(1).csv", sep = ",", header = T)
str(cancer_dat)
attach(cancer_dat)
table(cancervol)
table(weight)
table(age)
table(benpros)
table(vesinv)
table(capspen)
table(gleason)

```

```{r questionq}
fit0<-lm(psa~cancervol+weight+benpros+as.factor(vesinv)+capspen+gleason)
summary(fit0)
```

```{r b1}
fit01<-update(fit0,.~.-as.factor(vesinv))
anova(fit01,fit0)
```
so we can see the F-test value which is bigger than 0.05, we can't reject the $H_{0}$ that the vesian is not important.
```{r question1b}
#regress sale price on cancevol volume and weight
fit1<-lm(psa~cancervol+weight)
summary(fit1)
```
so from the summary of the regression on psa and cancervol and weight, we can get that the P-value for the cancervol estimator's significance is 1.08e-11 <0.05, which means that the estimator is needed, however the P-value for the weight estimator is 0.776>0.05, which means that the weight estimtor may not very significant.

```{r question1c}
#Add # age and #benpros and drop weight
fit2<-update(fit1,.~.-weight)
anova(fit2,fit1)
```
The F-test value is bigger than 0.05, so we can say that the weight estimator is unneeded.
```{r question2}
#Add  vesinv and capsen and drop age and benpros
fit3<-update(fit2,.~.+age)
summary(fit3)
```
From the summary given above, we can find that the P-value for age is bigger  than 0.929, so age may be unneeded.
```{r question3}
#drop vesinv and capspen and add gleason
fit4<-update(fit3,.~.-age)
anova(fit4,fit3)
```
from the summary we can find that the F value is bigger than 0.05, it means that the age is unneeded.
```{r question4}
fit5<-update(fit4,.~.+gleason)
summary(fit5)
```
we can see the gleason 's p value is bigger than the 0.05, so the glrason may be unneeded.
```{r l}
fit6<-update(fit5,.~.-gleason)
anova(fit6,fit5)
```
we can see that using F-test, the value is bigger than 0.05, so the gleason is unneeded.
```{r question1d}
# Residual plot

plot(fitted(fit6), resid(fit6))
abline(h=0)
#QQ plot
qqnorm(resid(fit6))
qqline(resid(fit6))
```
1.In the Residual plot it has no change on vertical spread so it is good models,
2.In the QQ norm plot,the normally assumption doesn't hold good, so we do some transform on the data.
```{r questionn}
#new qq plot after transformation,
fitn<-update(fit6,log(psa)~.)
qqnorm(resid(fitn))
qqline(resid(fitn))
```
it hold the normal assumption good aftertransormation
```{r test}
#use the best model to predict on sample mean
predictor<-mean(cancervol)
#compute the prdiction using coeficients
prediction<-fit6$coefficients[1]+fit6$coefficients[2]*predictor
prediction
```